---
title: "Team_7"
output:
  html_document: default
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

# Description

This document describes processes of data analysis of movie. The data
came from Kofic, which is Korean Film Council.

The data is available on the urls below:

-   all movies listed in Kofic
    (<https://www.kobis.or.kr/kobis/business/mast/mvie/searchMovieList.do>)

-   Data related with sales rev etc.
    (<https://www.kobis.or.kr/kobis/business/stat/offc/searchOfficHitTotList.do?searchMode=year>)

# Purpose

-   Identify impact of Covid-19 on Film Industry.
-   Identify significant factors that have effects on Box office.

# Data Cleaning

Before loading data, we use readxl package to load them

```{r}
#install.packages('readxl')
#install.packages('lubridate')
library(readxl)
library(lubridate)
library(dplyr)
library(ggplot2)
```

At first, load data To deal with Korean characters, this r codes are
encoded as 'utf-8'

If errors on loading data, reopen this document with 'utf-8'

```{r}
df <- read.csv('Movie Data.csv')
head(df)
```

Check types of variables in the data

```{r}
summary(df)
```

Not all columns are used in this analysis.

This Data have some duplicate columns.

It is because of merging different data into a file.

Change name of column to be used into English for easier processing.

```{r}
#colnames(df)

colnames(df)[1] <- 'Name'
colnames(df)[14] <- 'Release_Date'
colnames(df)[17] <- 'Nationality'
colnames(df)[18] <- 'Total_screens'
colnames(df)[19] <- 'Box_office'
colnames(df)[20] <- 'Audience'
colnames(df)[23] <- 'Genre'
colnames(df)[24] <- 'Rate'
colnames(df)[25] <- 'Artistic'

colnames(df)
```

Drop columns other than Name, Release Date, Nationality, Total Screens,
Box Office, Audience, Genre, Rate, Artistic

```{r}
df_edit_col <- df %>% select(Name, Release_Date, Nationality, 
                      Total_screens, Box_office, Audience,
                      Genre, Rate, Artistic)

colnames(df_edit_col)
```

Convert Release Date from numeric to as.Date

```{r}
df_edit_col$Release_Date <- ymd(df_edit_col$Release_Date)

class(df_edit_col$Release_Date)
```

Audience, Box office, Total screen are currently character value.

Convert Audience & Box Office & Total Screen into numerical value.

```{r}
df_edit_col$Audience <- as.numeric(df_edit_col$Audience)
df_edit_col$Box_office <- as.numeric(df_edit_col$Box_office)
df_edit_col$Total_screens <- as.numeric(df_edit_col$Total_screens)
```

Skip rows with NAs'

```{r}
df_skip_na <- na.omit(df_edit_col)

```

After, we identified rows with all 0s in Box Office, Audience, and \# of
screens.

We concluded that these are missing values or movies were listed on
Kofic but didn't be shown to the audience.

So, we skip these rows.

```{r}
df_skip_na_0s <- df_skip_na %>%
  filter(Total_screens > 0 & Box_office > 0 &Audience > 0)
```

Now we have 16506 rows X 9 columns data.

```{r}
nrow(df_skip_na_0s); ncol(df_skip_na_0s)
```

# Analysis

```{r}
library(lubridate)
library(dplyr)
```

### Impact of Covid19 on Movie Industry.

Covid 19 prevents people from gathering in a place. Lots of industries
have gotten damages. Film Industry is one of the damaged. In this part,
we are going to identify how much film industry is shrinked by looking
at Box Office by Year.

```{r}
df_byYear <- df_skip_na_0s
df_byYear$Year <- year(df_byYear$Release_Date)
```

```{r}
df_byYear <- df_byYear %>%
  group_by(Year) %>%
  summarise(Count = n(), Mean_Box_Office = mean(Box_office), Total_Box_Office = sum(Box_office))

df_byYear
```

Since 2009, Average Box Office per movie has been decreased. The time is
similar to introduction of smartphones. It can be a reason that people
can enjoy movies in their house through smart TVs and other devices. In
another way, it can be interpreted as Film Industry failed to compete
with competitors. Competitors are all industries related with
entertainment. Time is limited to all people so they cannot spend their
time to all entertaining industries.

In the decrease phase, Covid 19 crashed Revenue of Film Industry. In
2020, when Covid 19 got strongest power on the earth, Average Box Office
per Movie decreased by about 80%. It is the case that have never
happened before. Without preparation, Film Industry struggled in the
Covid effect. 2021 also doesn't look good. It has already passed half of
May but the Revenue is only half of the previous year. Film companies
not ready to get survived will meet the perish of themselves.

```{r}
ggplot(data = df_byYear,
       aes(x=Year, y=Mean_Box_Office, label = round(Mean_Box_Office/1000000000,2))) +
  geom_line(color = 'red') +
  geom_point()+
  labs(title="Average Box Office by Year in KRW Billion") +
  geom_text(size = 4, position = position_stack(vjust = 0.7))+
  theme(axis.text.x = element_text(size=13, angle=30, colour="black"),
        panel.background = element_rect(fill='white'),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "gray"))+
  scale_x_continuous(name=NULL, breaks=seq(2007,2021)) +
  scale_y_continuous(name=NULL, breaks=NULL)
```

## Linear Regression

For this part, we are going to identify relationship among Box Office
and other factors.

Before using linear regression, we are going to anticipate what factors
are significant for Box Office.

### Genre

In genre, we anticipate that Action and SF is significant for creating
better Box Office result. Action and Sf has characteristic of low burden
on watching them. Usually, People are not required to concentrate on a
movie when they are watching Action or Sf genres.

Because this data is recorded in Korean, we convert genre into English.

```{r}
df_byGenre <- df_skip_na_0s;
df_byGenre[df_byGenre['Genre']=='가족','Genre'] <- "Family"
df_byGenre[df_byGenre['Genre']=='공연','Genre'] <- "Play"
df_byGenre[df_byGenre['Genre']=='공포(호러)','Genre'] <- "Horror"
df_byGenre[df_byGenre['Genre']=='기타','Genre'] <- "Others"
df_byGenre[df_byGenre['Genre']=='다큐멘터리','Genre'] <- "Documentary"
df_byGenre[df_byGenre['Genre']=='드라마','Genre'] <- "Drama"
df_byGenre[df_byGenre['Genre']=='멜로/로맨스','Genre'] <- "Romans"
df_byGenre[df_byGenre['Genre']=='뮤지컬','Genre'] <- "Musical"
df_byGenre[df_byGenre['Genre']=='미스터리','Genre'] <- "Mystery"
df_byGenre[df_byGenre['Genre']=='범죄','Genre'] <- "Crime"
df_byGenre[df_byGenre['Genre']=='사극','Genre'] <- "Historic"
df_byGenre[df_byGenre['Genre']=='서부극(웨스턴)','Genre'] <- "Western"
df_byGenre[df_byGenre['Genre']=='성인물(에로)','Genre'] <- "Erotic"
df_byGenre[df_byGenre['Genre']=='스릴러','Genre'] <- "Thriller"
df_byGenre[df_byGenre['Genre']=='애니메이션','Genre'] <- "Animation"
df_byGenre[df_byGenre['Genre']=='액션','Genre'] <- "Action"
df_byGenre[df_byGenre['Genre']=='어드벤처','Genre'] <- "Adventure"
df_byGenre[df_byGenre['Genre']=='전쟁','Genre'] <- "War"
df_byGenre[df_byGenre['Genre']=='코미디','Genre'] <- "Comedy"
df_byGenre[df_byGenre['Genre']=='판타지','Genre'] <- "Fantasy"
table(df_byGenre$Genre)
```

looking at table(), we identified 0 values in genre. We ignore them.

```{r}
df_byGenre <- df_byGenre %>% filter(Genre != 0)

#table(df_byGenre$Genre)
df_byGenre <- df_byGenre %>%
  group_by(Genre) %>%
  summarise(Count = n(), Mean = mean(Box_office), Sum = sum(Box_office))
```

The result is quite different from our expectation. Historic has highest
Average Box Office among genres. Action and Sf is ranked at 4th and 6th
position.

The reason why Historic genre is powerful may that Historic genre has
wider range of audience than other genres. Not only 20-30s but also
50-60s are willing to watch these genres. 'Roaring Currents' has 17
million audiences, which is highest record in Korea. It is not possible
to attracting only 20-30s.

```{r}
ggplot(data= df_byGenre, aes(x=Genre, y=Mean, 
      label = round(Mean/1000000000,2)))+
  geom_bar(stat='identity', fill="orchid2", colour='black') +
  scale_x_discrete(name = NULL, 
                   limits = c("Historic", "Adventure", "Crime", "Action", "Fantasy", "SF", "Thriller"))+
  geom_text(size = 5, position = position_stack(vjust = 0.5))+
  scale_y_discrete(name = NULL) +
  theme(axis.ticks = element_blank()) +
  labs(title = "Average Box Office by Genre Part1.",
       subtitle="KRW Billion")+
  theme(axis.text.x = element_text(size = 12, colour='black'),
        panel.background = element_rect(fill='white'))
```

```{r}
ggplot(data= df_byGenre, aes(x=Genre, y=Mean, 
      label = round(Mean/1000000000,2)))+
  geom_bar(stat='identity', fill="orchid2", colour='black') +
  scale_x_discrete(name = NULL, 
                   limits = c("Comedy", "Mystery","Animation", "Drama", "Musical", "War", "Horror"))+
  geom_text(size = 5, position = position_stack(vjust = 0.5))+
  scale_y_discrete(name = NULL) +
  theme(axis.ticks = element_blank()) +
  labs(title = "Average Box Office by Genre Part2.",
       subtitle = "KRW Billion")+
  theme(axis.text.x = element_text(size = 12, colour='black'),
        panel.background = element_rect(fill='white'))
```

```{r}
ggplot(data= df_byGenre, aes(x=Genre, y=Mean, 
      label = round(Mean/1000000000,2)))+
  geom_bar(stat='identity', fill="orchid2", colour='black') +
  scale_x_discrete(name = NULL, 
                   limits = c("Family", "Romans", "Western","Documentary", "Play", "Others", "Erotic"))+
  geom_text(size = 5, position = position_stack(vjust = 0.5))+
  scale_y_discrete(name = NULL) +
  theme(axis.ticks = element_blank()) +
  labs(title = "Average Box Office by Genre Part3.",
       subtitle = "KRW Billion")+
  theme(axis.text.x = element_text(size = 12, colour="black"),
        panel.background = element_rect(fill='white'))
```

### Nationality

```{r}
df_byNation <- df_skip_na_0s
df_byNation <- df_byNation %>%
  group_by(Nationality) %>%
  summarise(Count = n(), Proportion = n()/nrow(df_byNation)*100,Mean_Box_Office = mean(Box_office), Sum = sum(Box_office))
```

looking at the data ordered by count, Korea, Japan and USA occupies
almost 80%. Therefore, we only focus on those three countries.

```{r}
df_byNation[order(df_byNation$Count, decreasing = T),]
```

As Korea and USA occupies significant percentage of all movies, they
have about Box office of KRW 2.7 Billion per movie. However, movies from
Japan only record KRW 0.07 Billion per movie. It can be a reason that
movies from Japan are mostly made for sexual arousal. They are not made
for attracting lots of people. On other hands, movies from USA recorded
higher average Box Office than from Korea. It can be a reason that most
of movies from USA are movies that recorded great success in the world
so distributors import them. In contrast, movies made in Korea are shown
themselves in Korea first. Some of them may not record success and some
may do.

```{r}
ggplot(data= df_byNation, aes(x=Nationality, y=Mean_Box_Office, 
      label = round(Mean_Box_Office/1000000000,2)))+
  geom_bar(stat='identity', fill="orchid2", colour='black') +
  scale_x_discrete(name = NULL, breaks = c("한국","미국","일본"), labels = c("Korea","USA","Japan"),limits=c("한국","미국","일본"))+
  geom_text(size = 5, position = position_stack(vjust = 0.8))+
  scale_y_discrete(name = NULL) +
  theme(axis.ticks = element_blank()) +
  labs(title = "Average Box Office by Nationality",
       subtitle = "KRW Billion")+
  theme(axis.text.x = element_text(size = 12, colour="black"),
        panel.background = element_rect(fill='white'))
```

### Rate

Rate has lots of levels but most of them are same meaning. It is derived
from modification of rating system for decades. To make chart, we need
to convert them into a consolidated level. We translated them into
seven:

-   All

-   Over 12

-   Over 15

-   Over 16

-   Over 18

-   Restricted

-   Not Decided

```{r}
df_byRate <- df_skip_na_0s
```

```{r}
df_byRate[df_byRate["Rate"] == '12세이상관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '국민학생관람불가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '전체관람가',"Rate"] = "All"
df_byRate[df_byRate["Rate"] == '15세관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '중학생이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '12세이상관람가,12세관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '18세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '18세관람가,15세이상관람가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '연소자관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '청소년관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '12세관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '15세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '고등학생이상관람가',"Rate"] = "Over_16"
df_byRate[df_byRate["Rate"] == '12세이상관람가,연소자관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '15세관람가,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '18세관람가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '미성년자관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '15세이상관람가,중학생이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '연소자관람가',"Rate"] = "All"
df_byRate[df_byRate["Rate"] == '고등학생이상관람가,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '연소자관람불가,청소년관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '연소자관람불가,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '18세관람가,청소년관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '미성년자관람가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '모든 관람객이 관람할 수 있는 등급,전체관람가',"Rate"] = "All"
df_byRate[df_byRate["Rate"] == '12세이상관람가,전체관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '12세이상관람가,고등학생이상관람가',"Rate"] = "Over_16"
df_byRate[df_byRate["Rate"] == '12세이상관람가,국민학생관람불가,15세이상관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '연소자관람가,전체관람가',"Rate"] = "All"
df_byRate[df_byRate["Rate"] == '청소년관람불가,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '모든 관람객이 관람할 수 있는 등급',"Rate"] = "All"
df_byRate[df_byRate["Rate"] == '12세이상관람가,15세이상관람가',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '12세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_12"
df_byRate[df_byRate["Rate"] == '12세이상관람가,15세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '12세이상관람가,중학생이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '15세이상관람가,미성년자관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '연소자관람가,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '청소년관람불가,12세관람가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '15세 미만인 자는 관람할 수 없는 등급 ,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '15세이상관람가,전체관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '15세이상관람가,18세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '국민학생관람불가,청소년관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '청소년관람불가,고등학생이상관람가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '고등학생이상관람가,청소년관람불가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '국민학생관람불가,15세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '15세관람가,12세이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '기타',"Rate"] = "Others"
df_byRate[df_byRate["Rate"] == '국민학생관람불가,중학생이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '미정',"Rate"] = "Not decided"
df_byRate[df_byRate["Rate"] == '청소년관람불가,전체관람가',"Rate"] = "Over_18"
df_byRate[df_byRate["Rate"] == '전체관람가,중학생이상관람가',"Rate"] = "Over_15"
df_byRate[df_byRate["Rate"] == '제한상영가',"Rate"] = "Restricted"
```

```{r}
table(df_byRate$Rate)
```

Movies rated as over 18 occupies half of the data but recorded lowest
average Box Office. It can be a reason that most of Japan movies are
made for sexual arousal so it occupies lots of proportion but record low
average Box Office. The highest average Box office is on Over 12
group.It may be because Over 12 can attract elementary school students
and their parents than Over 15 cannot do.

```{r}
df_byRate <- df_byRate %>%
  group_by(Rate) %>%
  summarise(Count = n(), Proportion = n()/nrow(df_byRate)*100,
            Mean_Box_Office = mean(Box_office),
            Sum_Box_Office = sum(Box_office))
```

```{r}
ggplot(data= df_byRate, aes(x=Rate, y=Mean_Box_Office, 
      label = round(Mean_Box_Office/1000000000,2)))+
  geom_bar(stat='identity', fill="orchid2", colour='black') +
  scale_x_discrete(name = NULL)+
  geom_text(size = 5, position = position_stack(vjust = 0.8))+
  scale_y_discrete(name = NULL) +
  theme(axis.ticks = element_blank()) +
  labs(title = "Average Box Office by Rate",
       subtitle = "KRW Billion")+
  theme(axis.text.x = element_text(size = 12, colour="black"),
        panel.background = element_rect(fill='white'))
```

### Artistic

Artistic Column has two values

-   Artistic

-   Not Artistic

These values are also written in Korea, we translate them into English.

```{r}
df_byArtistic <- df_skip_na_0s
table(df_byArtistic$Artistic)
```

```{r}
df_byArtistic[df_byArtistic["Artistic"]=="독립/예술영화","Artistic"] <- "Artistic"
df_byArtistic[df_byArtistic["Artistic"]=="일반영화","Artistic"] <- "Not_Artistic"
table(df_byArtistic$Artistic)
```

```{r}
df_byArtistic <- df_byArtistic %>%
  group_by(Artistic) %>%
  summarise(Count = n(), Proportion = n()/nrow(df_byArtistic)*100,
            Mean_Box_Office = mean(Box_office), Total_Box_Office = sum(Box_office))
```

As we can guess from their name, Artistic movies don't seem to generate
great success.

```{r}
ggplot(data= df_byArtistic, aes(x=Artistic, y=Mean_Box_Office, 
      label = round(Mean_Box_Office/1000000000,2)))+
  geom_bar(stat='identity', fill="orchid2", colour='black') +
  scale_x_discrete(name = NULL)+
  geom_text(size = 5, position = position_stack(vjust = 0.8))+
  scale_y_discrete(name = NULL) +
  theme(axis.ticks = element_blank()) +
  labs(title = "Average Box Office by Artistic",
       subtitle = "KRW Billion")+
  theme(axis.text.x = element_text(size = 12, colour="black"),
        panel.background = element_rect(fill='white'))
```

Based on analysis so far, we are going to check whether the result is
statistically significant through linear regression.

We set

-   Independent Variable

    -   Box Office

-   Dependent Variable

    -   Number of screens

    -   Nationality

    -   Audience

    -   Rate

    -   Genre

    -   Artistic

To prevent influencing raw data, we make a new data frame.

```{r}
df_regression <- df_skip_na_0s
```

When we checked Rate column, it has values with same meaning but
different expression.

It was derived from modification of rate system for time change.

We need to consolidate those expressions into one.

First, we need to check what kinds of ratings are in Rate column.

```{r}
unique(df_regression$Rate)
```

As did in rate analysis, we made consolidated level system.

```{r}
df_regression[df_regression["Rate"] == '12세이상관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '국민학생관람불가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '전체관람가',"Rate"] = "All"
df_regression[df_regression["Rate"] == '15세관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '중학생이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '12세이상관람가,12세관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '18세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '18세관람가,15세이상관람가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '연소자관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '청소년관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '12세관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '15세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '고등학생이상관람가',"Rate"] = "Over_16"
df_regression[df_regression["Rate"] == '12세이상관람가,연소자관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '15세관람가,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '18세관람가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '미성년자관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '15세이상관람가,중학생이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '연소자관람가',"Rate"] = "All"
df_regression[df_regression["Rate"] == '고등학생이상관람가,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '연소자관람불가,청소년관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '연소자관람불가,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '18세관람가,청소년관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '미성년자관람가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '모든 관람객이 관람할 수 있는 등급,전체관람가',"Rate"] = "All"
df_regression[df_regression["Rate"] == '12세이상관람가,전체관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '12세이상관람가,고등학생이상관람가',"Rate"] = "Over_16"
df_regression[df_regression["Rate"] == '12세이상관람가,국민학생관람불가,15세이상관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '연소자관람가,전체관람가',"Rate"] = "All"
df_regression[df_regression["Rate"] == '청소년관람불가,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '모든 관람객이 관람할 수 있는 등급',"Rate"] = "All"
df_regression[df_regression["Rate"] == '12세이상관람가,15세이상관람가',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '12세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_12"
df_regression[df_regression["Rate"] == '12세이상관람가,15세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '12세이상관람가,중학생이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '15세이상관람가,미성년자관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '연소자관람가,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '청소년관람불가,12세관람가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '15세 미만인 자는 관람할 수 없는 등급 ,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '15세이상관람가,전체관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '15세이상관람가,18세 미만인 자는 관람할 수 없는 등급',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '국민학생관람불가,청소년관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '청소년관람불가,고등학생이상관람가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '고등학생이상관람가,청소년관람불가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '국민학생관람불가,15세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '15세관람가,12세이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '기타',"Rate"] = "Others"
df_regression[df_regression["Rate"] == '국민학생관람불가,중학생이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '미정',"Rate"] = "Not decided"
df_regression[df_regression["Rate"] == '청소년관람불가,전체관람가',"Rate"] = "Over_18"
df_regression[df_regression["Rate"] == '전체관람가,중학생이상관람가',"Rate"] = "Over_15"
df_regression[df_regression["Rate"] == '제한상영가',"Rate"] = "Restricted"
```

For processing linear regression for categorical variable, it is needed
convert their values into separate columns.

Categorical variables what we use for this linear regression are Rate,
Genre, Nationality, Artistic. Make columns for each values in the
columns.

```{r}
df_regression$Over_12 = df_regression$Rate == 'Over_12'
df_regression$All = df_regression$Rate == 'All'
df_regression$Over_16 = df_regression$Rate == 'Over_16'
df_regression$Over_15 = df_regression$Rate == 'Over_15'
df_regression$Over_18 = df_regression$Rate == 'Over_18'
```

```{r}
unique(df_regression$Genre)
```

```{r}
df_regression$SF = df_regression$Genre == 'SF'
df_regression$Family = df_regression$Genre == '가족'
df_regression$Play = df_regression$Genre == '공연'
df_regression$Horror = df_regression$Genre == '공포(호러)'
df_regression$Others = df_regression$Genre == '기타'
df_regression$Documentary = df_regression$Genre == '다큐멘터리'
df_regression$Drama = df_regression$Genre == '드라마'
df_regression$Romans = df_regression$Genre == '멜로/로맨스'
df_regression$Musical = df_regression$Genre == '뮤지컬'
df_regression$Mystery = df_regression$Genre == '미스터리'
df_regression$Crime = df_regression$Genre == '범죄'
df_regression$Historic = df_regression$Genre == '사극'
df_regression$Western = df_regression$Genre == '서부극(웨스턴)'
df_regression$Erotic = df_regression$Genre == '성인물(에로)'
df_regression$Thriller = df_regression$Genre == '스릴러'
df_regression$Animation = df_regression$Genre == '애니메이션'
df_regression$Action = df_regression$Genre == '액션'
df_regression$Adventure = df_regression$Genre == '어드벤처'
df_regression$War = df_regression$Genre == '전쟁'
df_regression$Comedy = df_regression$Genre == '코미디'
df_regression$Fantasy = df_regression$Genre == '판타지'
```

```{r}
table(df_regression$Nationality)
```

Nationalities of USA, Japan, and Korea occupy most of the movies (about
80%) listed in Korea.

So, in this linear regression, we just focus on whether this movie is
made in USA, Japan, or Korea.

```{r}
df_regression[df_regression["Nationality"] == '미국',"Nationality"] = "USA"
df_regression[df_regression["Nationality"] == '한국',"Nationality"] = "Korea"
df_regression[df_regression["Nationality"] == '일본',"Nationality"] = "Japan"
```

```{r}
df_regression$USA = df_regression$Nationality == 'USA'
df_regression$Japan = df_regression$Nationality == 'Japan'
df_regression$Korea = df_regression$Nationality == 'Korea'
```

```{r}
unique(df_regression$Artistic)
```

We make new columns for Column: Artistic.

It has two values: Artistic or Not Artistic.

```{r}
df_regression[df_regression["Artistic"] == '독립/예술영화',"Artistic"] = "Artistic"
df_regression[df_regression["Artistic"] == '일반영화',"Artistic"] = "Not_artistic"
```

```{r}
df_regression$Artistic = df_regression$Artistic == 'Artistic'
df_regression$Not_artistic = df_regression$Artistic == 'Not_artistic'
```

Next, we are going to identify outliers for numerical variables.

```{r}
library(ggplot2)
```

1.  in Audience & Box_office

    It seems that we don't have outstanding values.

```{r}
ggplot(data=df_regression,aes(x=Audience, y=Box_office)) +
  geom_point()+
  scale_x_continuous(trans='log')+
  scale_y_continuous(trans='log')
```

2.  Number of Screens & Box Office

    values lower than 10 screens looks bizarre.

    we are going to drop those values for regression.

```{r}
ggplot(data=df_regression,aes(x=Total_screens, y=Box_office)) +
  geom_point()+
  scale_y_continuous(trans='log10')+
  scale_x_continuous(trans='log10')
```

```{r}
df_regression <- df_regression %>%
  filter(Total_screens > 10)
```

Box_office, Audience, Total_screens are too large than other variables
so that they can dominate the result.

so, we scale them using log base 10.

```{r}
df_regression$Box_log10 <- log(df_regression$Box_office, 10)
df_regression$Aud_log10 <- log(df_regression$Audience, 10)
df_regression$screen_log10 <- log(df_regression$Total_screens, 10)
```

Now, it's time to build regression model.

```{r}
Movie_reg <- lm(Box_log10 ~ Aud_log10 + screen_log10 +All + Over_12 + Over_15 + Over_16+ Over_18 + SF + Family + Play + Horror + Documentary + Drama + Romans + Musical + Mystery + Crime + Historic + Western + Erotic + Thriller + Animation + Action + Adventure + War + Comedy + Fantasy + USA + Japan + Korea + Artistic + Not_artistic, data=df_regression)

summary(Movie_reg)
```

#### Significant

\<0.1% level\>

-   Audience_log10

-   Screen_log10

-   AllTRUE

-   Over_12TRUE

-   Over_15TRUE

-   PlayTRUE

-   MusicalTRUE

-   EroticTRUE

-   JapanTRUE

-   KoreaTRUE

-   ArtisticTRUE

\<1% level\>

-   DocumentaryTRUE

\<5% level\>

-   MysteryTRUE

-   USATRUE

#### Interpretation

-   A one-percent increase in Audience increases Box Office by 1.00%.
-   A one-percent increase in number of screens increases Box Office by
    0.055%.
-   putting rate of All decreases Box office by an average of 0.1% as
    compared to without any rate
-   putting rate of Over 12 increases Box office by an average of 1.1%
    as compared to without any rate
-   putting rate of Over 15 increases Box office by an average of 1.3%
    as compared to without any rate
-   putting genre of Play increases Box office by an average of 46.7% as
    compared to without any genre
-   putting genre of Musical increases Box office by an average of 16.2%
    as compared to without any genre
-   putting genre of Erotic decreases Box office by an average of 13.5%
    as compared to without any genre
-   putting nationality of Japan increases Box office by an average of
    1.7% as compared to without any nationality
-   putting nationality of Korea decreases Box office by an average of
    2.3% as compared to without any nationality
-   putting Artistic increases Box office by an average of 4.5% as
    compared to without any Artistic or not
-   putting genre of Documentary increases Box office by an average of
    3.5% as compared to without any genre
-   putting genre of Mystery increases Box office by an average of 2.4%
    as compared to without any genre
-   putting nationality of USA increases Box office by an average of
    0.4% as compared to without any nationality
