---
title: "Team_7"
output: html_document
---
---Description----
This document describes processes of data analysis of movie.
The data came from Kofic, which is Korean Film Council.
The data is available on the urls below:
- all movies listed in Kofic (https://www.kobis.or.kr/kobis/business/mast/mvie/searchMovieList.do)
- Data related with sales rev etc.
(https://www.kobis.or.kr/kobis/business/stat/offc/searchOfficHitTotList.do?searchMode=year)

---Data Cleaning----
Before loading data, we use readxl package to load them
```{r}
#install.packages('readxl')
#install.packages('lubridate')
library(readxl)
library(lubridate)
library(dplyr)
```

At first, load data
this r codes are encoded as 'utf-8'
if errors on loading data, reopen this document with 'utf-8'
```{r}
df <- read_excel('(NEW2)(Merged) Movie Data.xlsx')
head(df)
```

Check data
```{r}
summary(df)
```
We saw unnecessary columns
Change name of column to english for easier processing
```{r}
#colnames(df)

colnames(df)[1] <- 'Name'
colnames(df)[14] <- 'Release_Date'
colnames(df)[17] <- 'Nationality'
colnames(df)[18] <- 'Total_screens'
colnames(df)[19] <- 'Box_office'
colnames(df)[20] <- 'Audience'
colnames(df)[23] <- 'Genre'
colnames(df)[24] <- 'Rate'
colnames(df)[25] <- 'Artistic'

colnames(df)
```

we decided to drop: column number 2~13, 15, 16, 21, 22
```{r}
df_edit_col <- df %>% select(Name, Release_Date, Nationality, 
                      Total_screens, Box_office, Audience,
                      Genre, Rate, Artistic)

#View(df_edit_col)
```

Convert Release Date from numeric to as.Date
```{r}
df_edit_col$Release_Date <- as.Date(myDf$Release_Date, origin='1900-01-01')

#df_edit_col$Release_Date

#View(df_edit_col)
```

We skip rows with NAs
```{r}
na.omit(df_edit_col)
```

