---
title: "Team_7"
output: html_document
---
---Description----
This document describes processes of data analysis of movie.
The data came from Kofic, which is Korean Film Council.
The data is available on the urls below:
- all movies listed in Kofic (https://www.kobis.or.kr/kobis/business/mast/mvie/searchMovieList.do)
- Data related with sales rev etc.
(https://www.kobis.or.kr/kobis/business/stat/offc/searchOfficHitTotList.do?searchMode=year)

---Data Cleaning----
Before loading data, we use readxl package to load them
```{r}
#install.packages('readxl')
#install.packages('lubridate')
library(readxl)
library(lubridate)
library(dplyr)
```

At first, load data
this r codes are encoded as 'utf-8'
if errors on loading data, reopen this document with 'utf-8'
```{r}
df <- read_excel('(NEW2)(Merged) Movie Data.xlsx')
head(df)
```

Check data
```{r}
summary(df)
```
We saw unnecessary columns
Change name of column to english for easier processing
```{r}
#colnames(df)

colnames(df)[1] <- 'Name'
colnames(df)[14] <- 'Release_Date'
colnames(df)[17] <- 'Nationality'
colnames(df)[18] <- 'Total_screens'
colnames(df)[19] <- 'Box_office'
colnames(df)[20] <- 'Audience'
colnames(df)[23] <- 'Genre'
colnames(df)[24] <- 'Rate'
colnames(df)[25] <- 'Artistic'

colnames(df)
```

we decided to drop: column number 2~13, 15, 16, 21, 22
```{r}
df_edit_col <- df %>% select(Name, Release_Date, Nationality, 
                      Total_screens, Box_office, Audience,
                      Genre, Rate, Artistic)

#View(df_edit_col)
```

Convert Release Date from numeric to as.Date
```{r}
df_edit_col$Release_Date <- as.Date(df_edit_col$Release_Date, origin='1900-01-01')

#df_edit_col$Release_Date

#View(df_edit_col)
```

We skip rows with NAs
```{r}
df_skip_na <- na.omit(df_edit_col)
```

After, we identified rows with all 0s in Box Office, Audience, and # of screens.
We concluded that these are missing values or movies didn't be shown to the audience.
So, we skip these rows.
```{r}
df_skip_na_0s <- df_skip_na %>%
  filter(Total_screens > 0 & Box_office > 0 &Audience > 0)
```

Now we have 16500 rows X 9 columns data.
```{r}
nrow(df_skip_na_0s); ncol(df_skip_na_0s)
```

--------------Analysis---------------
1. Linear Regression
for this part, we are going to identify relationship among Box Office and other factors.
We set
a)Independent Variable = Box Office
b)Dependent Variable = # of screens, Nationality, Audience, Rate, Genre, Artistic.

# of screen and Audience are already numeric values, so we don't need to modifying them.
However, Nationality, Genre, Rate and Artistic is characters. So we need to separate those values into each column.
```{r}
table(df$Nationality)
table(df$Genre)
table(df$Rate)
table(df$Artistic)
```

